Clone and graft:\\ Testing whole scientific applications as they are built

### 2014-11-26 turcksin-spring-mechanics/paper.tex
Update graph generation and figures. A bit more text.

\begin{wrapfigure}{L}{0.28\textwidth}
  \begin{center}
    \vspace*{-24pt}
    \includegraphics[width=0.25\textwidth]{figures/graph.png}
    \vspace*{-12pt}
  \end{center}
  \caption{\it Connection graph of the 144 tests that are part of the
    \aspect{} code base.}
  \vspace*{-3mm}
  \label{fig:aspect-tests}
\end{wrapfigure}
Finally, there are cases where you copy-paste pieces from multiple existing
tests into a new one, for example because you want to test the combination of
features for which you have already written individual testcases. At this
point, the metaphor of inheritance graphs starts to break down. However, in
practice, most tests are still closely related to some others. A visualization
of this for the 144 tests that are part of \aspect{}, each represented by a
dot, is shown in Fig.~\ref{fig:aspect-tests} where we draw tests farther apart
of there are more textual differences between the input files. Many tests come
in groups of 2, 3 or 4 that only differ in a few lines of input -- simple
modifications such as those between testcases 3, 4 and 5 above. On the other
hand, other group are further apart and are derived from different
examplars.

@@

In practice, once you have accumulated a number of testcases, running and
comparing them by hand using the commands above becomes unwieldy. In such
cases, it is useful to write little \texttt{Makefile}s that do this
automatically, or to use one of the tools available as open source -- for
example, the \texttt{CTest} program. It also
becomes more difficult to display tests that create difference when, for
example, you run the 7,000 tests of the \dealii{} testsuite. Again, there are
freely available systems such as \texttt{CDash} that present graphical
overviews of all succeeding and failing tests in a browser.

talk about a better naming scheme to make it easier to find test cases to clone

@@

>>>>

\begin{wrapfigure}{L}{0.45\textwidth}
  \begin{center}
    \vspace*{-24pt}
    \includegraphics[height=0.45\textwidth,angle=-90]{figures/graph.png}
    \vspace*{-12pt}
  \end{center}
  \caption{\it Connection graph of the 144 tests that are part of the
    \aspect{} code base.}
  \vspace*{-3mm}
  \label{fig:aspect-tests}
\end{wrapfigure}
Finally, there are cases where you copy-paste pieces from multiple existing
tests into a new one, for example because you want to test the combination of
features for which you have already written individual testcases. At this
point, the metaphor of inheritance graphs starts to break down. However, in
practice, most tests are still closely related to some others. A visualization
of this for the 144 tests that are part of \aspect{}, each represented by a
dot, is shown in Fig.~\ref{fig:aspect-tests} where we draw tests farther apart
of there are more textual differences between the input files. Many tests come
in groups of 2, 3 or 4 that only differ in a few lines of input -- simple
modifications such as those between testcases 3, 4 and 5 above. On the other
hand, other group are further apart and are derived from different
examplars.

The message from this section, though, is that in almost all cases writing a
new testcase is actually really easy: find a good starting point, copy it,
make minor modifications and additions, and verify the output. Testing
scientific codes really doesn't have to be hard!

@@

In practice, once you have accumulated a number of testcases, you will
encounter practical difficulties. First, when you try to find the right
starting point to clone and graft a new testcase, you will not recall if
\texttt{tests/testcase-3.json} or \texttt{tests/testcase-5.json} is the one
that's closest to the situation you have in mind (for example, if you want to
augment your model and you are looking again for a testcase with equal masses
and friction coefficients).

In our experience, using more descriptive filenames for the input files has
helped, as is placing comments at the top of each input file describing what
the test does or, if appropriate, how it differs from a previous
testcase. Many of our testcases in \aspect{} have names like
\texttt{tests/melt-fraction-peridotite.prm} and comments at the top of the
form ``\textit{Like the melt-fraction.prm test, but using the peridotite
  material parameters.}''

Second, running and
comparing many tests by hand using the commands above becomes unwieldy. In such
cases, it is useful to write little \texttt{Makefile}s that do this
automatically, or to use one of the tools available as open source -- for
example, the \texttt{CTest} program. It also
becomes more difficult to display tests that create difference when, for
example, you run the 7,000 tests of the \dealii{} testsuite. Again, there are
freely available systems such as \texttt{CDash} that present graphical
overviews of all succeeding and failing tests in a browser.

@@

\section{Conclusions}
